API design for machine learning software: experiences from the scikit-learn project

### 2013-06-27 paper.tex
rename first section Introduction
"The scikit-learn project" also starts off the first sentence,
and the first sentence of the abstract.
split long paragraph
Cosmit.

\section{The scikit-learn project}

@@

\texttt{Pipeline} objects chain multiple estimators into a single one. This is
useful since a machine learning workflow typically involves a fixed sequence of
processing steps (e.g., feature extraction, dimensionality reduction, learning
and making predictions), many of which perform some kind of learning.
A sequence of $N$ such steps can be combined into a
\texttt{Pipeline} if the first $N-1$ steps are transformers; the last can be
either a predictor, a transformer or both. Conceptually, fitting a pipeline to
a training set amounts to the following recursive procedure: i) when only one
step remains, call its \texttt{fit} method; ii) otherwise, \texttt{fit} the
first step, use it to \texttt{transform} the training set and \texttt{fit} the
rest of the pipeline with the transformed data. The pipeline exposes all the
methods the last estimator in the pipe exposes. That is, if the last estimator
is a predictor, the pipeline can itself be used as a predictor. If the last
estimator is a transformer, then the pipeline is itself a transformer.

@@

\section{Future directions}
\label{sec:future_work}
There are several directions that the \sklearn project
aims to focus on in future development.
At present, the library does not support some classical machine learning
algorithms,
including neural networks, ensemble meta-estimators for
bagging or subsampling strategies and missing value completion algorithms.
Tasks like structured prediction or reinforcement learning are
considered off-scope for the project, since they would require quite different
data representations and APIs.

>>>>

\section{Introduction}

@@

\texttt{Pipeline} objects chain multiple estimators into a single one. This is
useful since a machine learning workflow typically involves a fixed sequence of
processing steps (e.g., feature extraction, dimensionality reduction, learning
and making predictions), many of which perform some kind of learning.
A sequence of $N$ such steps can be combined into a
\texttt{Pipeline} if the first $N-1$ steps are transformers; the last can be
either a predictor, a transformer or both.

Conceptually, fitting a pipeline to
a training set amounts to the following recursive procedure: i) when only one
step remains, call its \texttt{fit} method; ii) otherwise, \texttt{fit} the
first step, use it to \texttt{transform} the training set and \texttt{fit} the
rest of the pipeline with the transformed data. The pipeline exposes all the
methods the last estimator in the pipe exposes. That is, if the last estimator
is a predictor, the pipeline can itself be used as a predictor. If the last
estimator is a transformer, then the pipeline is itself a transformer.

@@

\section{Future directions}
\label{sec:future_work}
There are several directions that the \sklearn project
aims to focus on in future development.
At present, the library does not support some classical machine learning
algorithms,
including neural networks, ensemble meta-estimators for
bagging or subsampling strategies and missing value completion algorithms.
However, tasks like structured prediction or reinforcement learning are
considered off-topic for the project, since they would require quite different
data representations and APIs.
